<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  cache = FALSE,
  message = TRUE
)
```

# plogr

Provides the header files for the [plog](https://github.com/SergiusTheBest/plog) header-only C++ logging library, and a method to log to R's standard error stream.


## Installation

You can install `plogr` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("krlmlr/plogr")
```

## Example

The code shows a small usage example and a demo which we'll call from R below.
For further details consult the [plog documentation](https://github.com/SergiusTheBest/plog#readme).

```{Rcpp}
// [[Rcpp::depends(plogr)]]
#include <Rcpp.h>
#include <plogr.h>

// [[Rcpp::export]]
void plogr_demo() {
  LOG_INFO << "test 1";
  plog::init_r(plog::info);
  LOG_INFO << "test 2";
  LOG_DEBUG << "test 3";
}
```

The R code below calls the `plogr_demo()` C++ function defined above.
Currently, the messages are printed straight to the standard error, so the message capturing mechanisms employed by `knitr` don't work.
We use a sink with a text connection to capture the messages, and print the contents of the variable to which the text connection assigns.


```{r}
output <- character()
con <- textConnection("output", "a")
withr::with_message_sink(con, plogr_demo())
close(con)
output
```

Nothing happens before we actually initialize the logger.
Because it is initialized to the `info` level, the debug log message is swallowed.
